# Read the dataset and show the variables

```{r}
wine <- read.csv(file = "/datasets/winequality.csv")
head (wine)
```
# Summary of the dateset for statistical view and to explore if there is any NA values

```{r}
summary(wine)
```
# Plot bar charts to view the distribution of Type (red = 1 and white = 2)

```{r}
barplot(table(wine$Type))
```
```{r}
barplot(table(wine$quality))
```
# Categorizing the quality variable to new variable taste

```{r}
wine$taste <- ifelse(wine$quality < 6, 'bad', 'good')
wine$taste[wine$quality == 6] <- 'normal'
wine$taste <- as.factor(wine$taste)
head (wine)
```
```{r}
table(wine$taste)
```
# Factorized the variables that need to be categorized

```{r}
str(wine)
```

# Normalization of the data as there are differnece in the scale

```{r}
normalize <- function(x) {return ((x - min(x)) / (max(x) - min(x)))}
normwine <- as.data.frame(lapply(wine[0:11], normalize))
summary(normwine$radius)
```
```{r}
normwine
```
# Feature selection
  # install and load the libraries
  
```{r}
install.packages("mlbench")
library(mlbench)
install.packages("caret")
library(caret)
```
# Calculate correlation matrix 
  
```{r}
set.seed(7)
correlationMatrix <- cor(normwine[,0:11])
# summarize the correlation matrix
print(correlationMatrix)
# find attributes that are highly corrected (ideally >0.75)
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.5)
# print indexes of highly correlated attributes
print(highlyCorrelated)
```
# Rank Features By Importance
```{r}
control <- trainControl(method="repeatedcv", number=10, repeats=3)
# train the model
model <- train(taste~., data=normwine, method="lvq", preProcess="scale", trControl=control)
# estimate variable importance
importance <- varImp(model, scale=FALSE)
# summarize importance
print(importance)
# plot importance
plot(importance)
```
# Model to check from here

```{r}
set.seed(123)
samp <- sample(nrow(wine), 0.6 * nrow(wine))
train <- wine[samp, ]
test <- wine[-samp, ]

```
```{r}
library(randomForest)
model <- randomForest(taste ~ . - quality, data = train)
```
```{r}
model
```
```{r}
pred <- predict(model, newdata = test)
table(pred, test$taste)
```
```{r}
(482 + 252 + 667) / nrow(test)
```
